---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE, fig.width=8, fig.height=6)

```

```{css}
body {
  font-family: monospace;
  color: #1a1f4b;
  line-height: 1.7;
}

h1, h2, h3 {
  font-family: monospace;
  color: #2a47b8;
  border-bottom: 1px solid #b0c0f0;
  padding-top: 6px;
  padding-bottom: 6px;
}

code, pre {
  background-color: #d0dcff;
  color: #1a2d99;
  border-radius: 6px;
  padding: 2px 5px;
}

pre {
  padding: 10px 10px;
  border-left: 3px solid #2a47b8
}

img {
  width: 500px;
  padding-top: 6px;
  padding-bottom: 6px;
}
```

## Is there a relationship between the genre and the activity when listening to music?

```{r}
library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTgb1yzwsWNeOE_--GWrU73P2LBw12eQQvGFqs68XmbmYHjPz9il8iQhDDU3-HzvquKo8IGyRJQcMi5/pub?gid=1632617460&single=true&output=csv")

latest_data <- logged_data %>%
  rename(time = 2,
         length = 3,
         genre = 4,
         activity = 5)

median_length <- median(latest_data$length)
total_length  <- sum(latest_data$length)  

num_sessions <- nrow(latest_data)

latest_data %>%
  ggplot() + 
  geom_bar(aes(x = genre),
           fill = "#FF6961") +
    labs(title = "Genres listened to",
       subtitle = "Comparing the counts of different genres",
       caption = "Source: Google Forms",
       x = "Genre of music listened",
       y = "Number of times this genre was listened to")

latest_data %>%
  ggplot() + 
  geom_bar(aes(x = activity),
               fill = "#87CEEB") +
  labs(title = "Activity done when listening to music",
       subtitle = "Comparing the counts of the activity done when listening to music",
       caption = "Source: Google Forms",
       x = "Activity when listening to music",
       y = "Number of times activity was performed")

latest_data %>%
  ggplot() + 
  geom_bar(aes(x = activity,
               fill = genre)) +
  labs(title = "Different song moods for different activities?",
       subtitle = "Comparing genre and activity when listening to music based on personal logs",
       caption = "Source: Google Forms",
       x = "Activity when listening to music",
       y = "Number of times activity was performed")

```


During a period of 7 days, I recorded `r num_sessions` sessions of listening to music with a median session length of `r median_length` minutes and a total of `r total_length` (`r total_length / 60` hours and `r total_length % 60`minutes over the 7 days. The below charts summarise data related to genre and the activity I was doing when I listened to music.  

