---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  font-family: monospace;
  color: #1a1f4b;
  line-height: 1.7;
}

h1, h2, h3 {
  font-family: monospace;
  color: #1db954;
  padding-top: 6px;
}

img {
  width: 500px;
  padding-top: 6px;
  padding-bottom: 6px;
}
```

## Are there any patterns existing in my music listening habits?

Given the logged data from recorded music listening sessions, I will investigate if there are any patterns that exist between the time, the activity, the session length, and the genre when I listened to music. 

```{r}
library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTgb1yzwsWNeOE_--GWrU73P2LBw12eQQvGFqs68XmbmYHjPz9il8iQhDDU3-HzvquKo8IGyRJQcMi5/pub?gid=1632617460&single=true&output=csv")

latest_data <- logged_data %>%
  rename(time = 2,
         length = 3,
         genre = 4,
         activity = 5)

```

```{r}
median_length <- median(latest_data$length)
total_length  <- sum(latest_data$length)
num_sessions <- nrow(latest_data)

latest_data %>%
  ggplot() +
  geom_bar(aes(x = time,
               fill = genre)) +
  labs(title = "Does time of day affect genre choice?",
       subtitle = "Comparing genre choice and the time of day I listened to music",
       caption = "Source: Google Forms",
       x = "Time of day",
       y = "Number of sessions")

latest_data %>%
  ggplot() + 
  geom_bar(aes(x = time,
               fill = activity)) +
  labs(title = "Does time of day affect the type of activity I partake in when listening to music?",
       subtitle = "Comparing time and activity when listening to music based on personal logs",
       caption = "Source: Google Forms",
       x = "Time of day",
       y = "Number of sessions")

latest_data %>%
  ggplot() + 
  geom_bar(aes(x = activity,
               fill = genre)) +
  labs(title = "Does the activity being partaken in affect genre choice?",
       subtitle = "Comparing genre and activity when listening to music based on personal logs",
       caption = "Source: Google Forms",
       x = "Activity when listening to music",
       y = "Number of times activity was performed")

```

### Summary of values

During a period of 7 days, I recorded `r num_sessions` sessions of listening to music with a median session length of `r median_length` minutes and a total of `r total_length` minutes (`r floor(total_length / 60)` hours and `r total_length %% 60` minutes) over the 7 days. 

### Graph further investigation

The above charts summarise data related to genre, time of day, and the activity I was doing when I listened to music. They reveal clear patterns on my genre choice and how it changes depending on the activity I am partaking in or the time of day.   

The first graph suggests that I tend to listen to Chinese R&B and KPOP more during the evening, while during the late night, I prefer Lo-fi and KPOP. It also shows that I am more likely to listen to chill/bedroom R&B in the mornings/afternoon versus evening/late night. Moreover, I only ever listen to English pop during the mornings and afternoon. 

My second graph shows that during the late night, I am mostly studying when listening to music, while my third graph shows that when I am studying, I mainly listen to KPOP, with Lo-fi being the second most played genre. This leads to an interesting idea - with Lo-fi being a non verbal genre, and KPOP being a non-English genre, it could mean that I am able to focus more when I listen to them. Additionally, I only listen to music in the morning when I am getting ready to head out, which may explain why I listen to English pop the most in the morning - I could be wanting music that hypes me up more to start the day. 

Moreover, my third graph shows that I tend to listen to R&B music when I am commuting - whether that be Chinese R&B or chill/bedroom R&B. This is pretty interesting, as I means I tend to reach for music that is more "chill" or "vibey" during this activity. 


